\begin{thebibliography}{10}
	\expandafter\ifx\csname url\endcsname\relax
	  \def\url#1{\texttt{#1}}\fi
	\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
	\expandafter\ifx\csname href\endcsname\relax
	  \def\href#1#2{#2} \def\path#1{#1}\fi
	
	\bibitem{Crypto_Bases}
		Koblitz N., A Course in Number Theory and Cryptography(1994), Graduate Texts in Mathematics, Springer, New York
		
	\bibitem{Crypto_Bases2}
		Nigel Paul Smart, Cryptography: An Introduction(2003), Mcgraw-hill education, McGraw-Hill, Univeristy of California
	
	\bibitem{Shannon}
		Shannon, C. E. (1945). A mathematical theory of cryptography. Mathematical Theory of Cryptography.
	
	\bibitem{Art_of_Secrecy}
		Charbathia, S. \& Sharma, S. (2014) A Comparative Study of Rivest Cipher Algorithms. International Journal of Information \& Computation Technology.
	
	\bibitem{Feistel_Def}
		\texttt{Feistel cipher.} Wikipedia, the free encyclopedia.\\
			\url{https://en.wikipedia.org/wiki/Feistel_cipher}
	
	\bibitem{SP_Def}
			\texttt{Substitution-permutation network.} Wikipedia, the free encyclopedia.\\
				\url{https://en.wikipedia.org/wiki/Substitution%E2%80%93permutation_network}
		
	\bibitem{DES_Lin}
		Matsui M. (1994) Linear Cryptanalysis Method for DES Cipher. In: Helleseth T. (eds) Advances in Cryptology — EUROCRYPT ’93. EUROCRYPT 1993. Lecture Notes in Computer Science, vol 765. Springer, Berlin, Heidelberg\\
	
	\bibitem{DES_Diff}
			Biham E., Shamir A. (1993) Differential Cryptanalysis of the Full 16-Round DES. In: Differential Cryptanalysis of the Data Encryption Standard. Springer, New York, NY\\
		
	\bibitem{DES_Diff2}
		Coppersmith, D. (May 1994). The Data Encryption Standard (DES) and its strength against attacks (PDF). IBM Journal of Research and Development.
	
	\bibitem{Diff-Lin_Def}
			\texttt{Differential-linear attack.} Wikipedia, the free encyclopedia.\\
				\url{https://en.wikipedia.org/wiki/Differential-linear_attack}
	
	\bibitem{Twofish_attack}
		\texttt{Twofish Cryptanalysis Rumors.} Schneier on Security.\\
			\url{https://www.schneier.com/blog/archives/2005/11/twofish_cryptan.html}
	
	\bibitem{TFG_M-Verona}
		Verona, Marta (September 2018). Criptografía en sistemas de mensajería instantánea(PDF). Universidad de Granada.
		\url{https://core.telegram.org/api/end-to-end}
	
	\bibitem{AES_process}
		\texttt{Cryptographic Standards and Guidelines.} NIST Computer Security Resource Center.\\
			\url{https://csrc.nist.gov/projects/cryptographic-standards-and-guidelines/archived-crypto-projects/aes-development}
			\url{https://csrc.nist.gov/CSRC/media/Projects/Cryptographic-Standards-and-Guidelines/documents/aes-development/R2comments.pdf}
	
	\bibitem{AES_Round1}
		Nechvatal, J., Barker, E., Dodson, D., Dworkin, M., Foti, J., \& Roback, E. (1999). Status report on the first round of the development of the Advanced Encryption Standard. Journal of Research of the National Institute of Standards and Technology.
	
	\bibitem{Square_Official}
		Joan Daemen; Lars Knudsen; Vincent Rijmen (1997). The Block Cipher Square (PDF). Fast Software Encryption (FSE) 1997, Volume 1267 of Lecture Notes in Computer Science. Haifa, Israel: Springer-Verlag. pp. 149–165. Retrieved 2007-02-15
	
	\bibitem{Square_Wiki}
		\texttt{Square (cipher).} Wikipedia, the free encyclopedia.\\
			\url{https://en.wikipedia.org/wiki/Square_(cipher)}
	
	\bibitem{Rijndael_AES_process}
		Daemen J., Rijmen V. (2002) The Advanced Encryption Standard Process. In: The Design of Rijndael. Information Security and Cryptography (Texts and Monographs). Springer, Berlin, Heidelberg

	\bibitem{Rijndael_specs}
		Daemen J., Rijmen V. (2002) Specification of Rijndael. In: The Design of Rijndael. Information Security and Cryptography (Texts and Monographs). Springer, Berlin, Heidelberg

	\bibitem{Rijndael_design}
		Daemen J., Rijmen V. (2002) Design Philosophy. In: The Design of Rijndael. Information Security and Cryptography (Texts and Monographs). Springer, Berlin, Heidelberg
	
	\bibitem{Rijndael_AES}
		Joan Daemen, Vincent Rijmen, AES Proposal: Rijndael, Proton World Int.l, Belgium, Katholieke Universiteit Leuven, Belgium,  September 1999 \\
	
	\bibitem{Rijndael_crypto}
		Daemen J., Rijmen V. (2002) Cryptanalysis. In: The Design of Rijndael. Information Security and Cryptography (Texts and Monographs). Springer, Berlin, Heidelberg
	
	\bibitem{Implementations}
			\texttt{Source Code.} Schneier on Security.\\
				\url{https://www.schneier.com/books/applied_cryptography/source.html}
		
	\bibitem{Crypto}
		\texttt{Crypto++ Library 7.0} Official Library Documentation
			\url{https://www.cryptopp.com/wiki/Advanced_Encryption_Standard}
			\url{https://www.cryptopp.com/wiki/Serpent}
			\url{https://www.cryptopp.com/wiki/Twofish}
			\url{https://www.cryptopp.com/wiki/Rc6}
	
	\bibitem{DES_Boxes}
		\texttt{DES supplementary material.} Wikipedia, the free encyclopedia.\\
			\url{https://en.wikipedia.org/wiki/DES_supplementary_material}
	
	\bibitem{FPGA_Finalists}
		AJ Elbirt, W Yip, B Chetwynd, C Paar. IEEE Transactions on Very Large Scale Integration (VLSI) Systems 9 (4), 545-557 \\

	\bibitem{Serpent_AES}
		Ross Anderson, Eli Biham, Lars Knudsen, Serpent: A Proposal for the Advanced Encryption Standard, Cambridge University, England; Technion, Haifa, Israel; University of Bergen, Norway \\
	
	\bibitem{MARS_Alg}
		C Burwick, D Coppersmith, E D’Avignon, R Gennaro, S Halevi, C Jutla, S M Matyas, L O’Connor, M Peyravian, D Safford, others (1999) The MARS Encryption Algorithm. NIST AES Proposal, Citeseer, 1998 \\
	
	\bibitem{MARS_AES}
		C Burwick, D Coppersmith, E D’Avignon, R Gennaro, S Halevi, C Jutla, S M Matyas Jr, L O’Connor, M Peyravian, D Safford, others (1999) MARS - a candidate cipher for AES. NIST AES Proposal, Citeseer, 1998 \\
	
	\bibitem{BlowfishWiki}
		\texttt{Blowfish (cipher).} Wikipedia, the free encyclopedia.\\
		\url{https://en.wikipedia.org/wiki/Blowfish_(cipher)}
	
	\bibitem{TwoFish_AES}
		B. Schneier, J. Kelsey, D. Whiting, D. Wagner, C. Hall, and N. Ferguson (1998) Twofish: A 128-Bit Block Cipher.

	\bibitem{TwoFish_KeyS}
		B. Schneier, J. Kelsey, D. Whiting, D. Wagner, C. Hall, and N. Ferguson (1998) On the Twofish Key Schedule.

	\bibitem{TwoFish_FPGA}
		Pawel Chodowiec, Kris Gaj (1999) Implementation of the Twofish Cipher Using FPGA Devices. Technical Report Electrical and Computer Engineering, George Mason University.
	
	\bibitem{TwoFish_Apps}
		\texttt{Twofish Cryptanalysis Rumors.} Schneier on Security.\\
			\url{https://www.schneier.com/academic/twofish/products.html}

	\bibitem{RC6_Family}
		S. Charbathia, and S. Sharma (2014). A Comparative Study of Rivest Cipher Algorithms. International Journal of Information \& Computation Technology.
	
	\bibitem{RC6_AES}
		R. L. Rivest, M. J. Robshaw, R. Sidney and Y. L. Yin (1998). The RC6\texttrademark \space block cipher. First Advanced Encryption Standard (AES) Conference.

	\bibitem{RC6_Crypt}
		R. L. Rivest, M. J. Robshaw, R. Sidney and Y. L. Yin (1998). The Security of RC6\texttrademark \space block cipher. NIST AES SUBMISSION.

\end{thebibliography}